\section*{Publications}

\begin{ilist}

\item Dhavale, S., and A. Aiyyer (2025): The Structure of a Developing Arabian Sea Monsoon Onset Vortex: Role of Moist Convection. J. Atmos. Sci., https://doi.org/10.1175/JAS-D-24-0212.1. 

\item Hwang, J. , C. J. Schreck III, A. Aiyyer, A. Sankarasubramanian (2025), Understanding the organizing scales of winter flood hydroclimatology and the as sociated drivers over the coterminous United States, Journal of Hydrology, 27. https://doi.org/10.1016/j.hydroa.2025.100200.

\item Hasan, M., S. M. Larson, K. McMonigal, W. A. Robinson, and A. Aiyyer (2024): Hemisphere-Dependent Impacts of ENSO and Atmospheric Eddies on Hadley Circulation. J. Climate, 37, 6533–6548.  https://doi.org/10.1175/JCLI-D-24-0112.1. 
  
\item  Aiyyer, A., and Schreck, C. (2023). Surface wind speeds and enthalpy fluxes during tropical cyclone formation from easterly waves: A CYGNSS view. Geophysical Research Letters, 50, e2022GL100823. https://doi.org/10.1029/2022GL100823
  
\item Aiyyer, A. and Wade. T. (2021). Acceleration of Tropical Cyclones As a Proxy For Extratropical
Interactions: Synoptic-Scale Patterns and Long-Term Trends. Weather Clim. Dynam. Discuss., https://wcd.copernicus.org/preprints/wcd-2021-4/

\item White J. D., Aiyyer, A., and Russell, J. O. H., Aiyyer, A. (2021). The Impact of Orography on the African Easterly Wave Stormtrack.  \emph{J. Geophys. Res.}, https://doi.org/10.1029/2020JD033749.
  

\item Mantripragada, R S. S., Schreck III, C. J. and Aiyyer, A., 2021. Energetics of Interactions between African Easterly Waves and Convectively Coupled Kelvin Waves.  \emph{Mon. Wea. Rev.}, 149(11), 3821-3835.  https://doi.org/10.1175/MWR-D-21-0003.1.

\item Chalise, D. R., Aiyyer, A., and Sankarasubramanian, A. (2021). Tropical cyclones’ contribution to seasonal precipitation and streamflow over the southeastern and southcentral United States. Geophysical Research Letters, 48, e2021GL094738. https://doi.org/10.1029/2021GL094738
  
\item White J. D. and A. Aiyyer, 2021: African Easterly Waves in an Idealized General Circulation Model: Instability and Wavepacket Diagnostics, Weather Clim. Dynam. Discuss, https://doi.org/10.5194/wcd-2020-47.
 
\item Russell, J.O. and A. Aiyyer, 2020: The Potential Vorticity Structure and Dynamics of African Easterly Waves. J. Atmos. Sci., 0, https://doi.org/10.1175/JAS-D-19-0019.1.

\item Russell, J. O. H., Aiyyer, A., and White, J. D. 2020. African easterly wave dynamics in convection‐permitting simulations: Rotational stratiform instability as a conceptual model. \emph{Journal of Advances in Modeling Earth Systems}, 12, e2019MS001706.
  
\item Hannah W. and A. Aiyyer 2017: Reduced African Easterly Wave Activity with Quadrupled
  CO2 in the Super-Parameterized CESM, \emph{J. Clim.},30, 8253-8274

\item Russell, J. O., A. Aiyyer, J. D. White and W. Hannah 2016:Revisiting the connection between African Easterly Waves and Atlantic tropical cyclogenesis.  \emph{Geophys.Res. Lett.}, 44, 587-595.

\item A. Aiyyer, 2015: Recurving Western North Pacific Tropical Cyclones and Mid-Latitude Predictability. \emph{Geophys. Res. Lett.}, 7799-7807.

\item Diaz, M. and A. Aiyyer, 2015: Absolute and Convective Instability of the African Easterly Jet. \emph{J. Atmos. Sc.}, 72., 1805-1826
  
\item Tyner, B., A. Aiyyer, J. Blaes, and D. R. Hawkins 2015: A Climatological Examination of
Sustained Wind Speeds, Wind Gusts and Wind Forecasts for Recent Tropical Cyclones in the
Mid-Atlantic Region of the United States. \emph{Wea. Forecasting}, 30, 153-176


\item Diaz, M. and A. Aiyyer, 2013: Genesis of African Easterly Waves by Upstream Energy Dispersion. \emph{J. Atmos. Sc.}, 70, 3492–3512. 

\item Mallard, M., G. M. Lackmann and A. Aiyyer, 2013: Atlantic Hurricanes and Climate Change. Part II: Role of Thermodynamic Changes in Decreased Hurricane Frequency. \emph{J. Clim.} 26, 8513–8528

\item Mallard, M., G. M. Lackmann, A. Aiyyer, K. Hill, 2013: Atlantic Hurricanes and Climate Change. Part I: Experimental Design and Isolation of Thermodynamic Effects. \emph{J. Clim.}, 26, 4876-4893.

\item Tyner, B. P. and A. Aiyyer, 2012: Evolution of African Easterly Waves in Isentropic Potential Vorticity Fields. \emph{Mon. Wea. Rev.}, 140, 3634-3652.

\item Aiyyer, A., A. Mekonnen and C. Shreck-III, 2012: Projection of Tropical Cyclones on Wavenumber Frequency Filtered Equatorial Waves. \emph{J. Clim.}, 25, 3653-3658.

\item Schreck, C., J. Molinari and A. Aiyyer, 2012: A Global View of Equatorial Waves and Tropical Cyclogenesis. \emph{Mon. Wea. Rev.}, 140, 774-788.


\item Aiyyer A. and C. Thorncroft, 2011: Interannual to multidecadal variability of vertical shear in the tropics. \emph{J. Clim.}, 24, 2949-2962.

\item Novak. D. R., B. A. Colle and A. R. Aiyyer, 2010: Evolution of Mesoscale Precipitation Band Environments within the Comma Head of Northeast U.S. Cyclones. Mon. Wea. Rev., 138, 2354-2374. 

\item N. Meskhidze, L. A. Remer, S. Platnick, R. Negron Juarez, A. M. Lichtenberger, and A. R. Aiyyer (2009), Exploring the differences in cloud properties observed by the Terra and Aqua MODIS sensors, \emph{Atmos. Chem. Phys. Discuss.}, 9, 1489-1520.

\item Galarneau, T. J., Jr., L. F. Bosart, and A. R. Aiyyer, 2008: Closed anticyclones of the subtropics and middle latitudes: A 54-yr climatology (1950-2003) and three case studies. Synoptic-Dynamic Meteorology and Weather Analysis and Forecasting: A Tribute to Fred Sanders, Meteor. Monogr., No. 55, Amer. Meteor. Soc., 349-392.

\item Aiyyer, A. R., and J. Molinari, 2008: MJO and Tropical Cyclogenesis in the Gulf of Mexico and Eastern Pacific: Case Study and Idealized Numerical Modeling. \emph{J. Atmos. Sci.}, 65, 2837-2855. 

\item Archambault, H. M., L. F. Bosart, D. Keyser, and A. R. Aiyyer, 2008: Influence of Large-Scale Flow Regimes on Cool-Season Precipitation in the Northeastern United States. \emph{Mon. Wea. Rev.}, 136, 2945-2963. 

\item Mekonnen, A., C. D. Thorncroft, A. R. Aiyyer, and G. N. Kiladis, 2008: Convectively coupled Kelvin waves over tropical Africa during the boreal summer: Structure and variability. \emph{J. Clim.}, 21, 6649-6667.

\item Holder, C. T., S. Yuter, A. H. Sobel, and A. R. Aiyyer, 2008:The Mesoscale Characteristics of Tropicalholder Oceanic Precipitation during Kelvin and Mixed Rossby-Gravity Wave Events. \emph{Mon. Wea. Rev.}, 136, 3446-3464. 

\item Atallah, E., L. F. Bosart, and A. R. Aiyyer, 2007: Precipitation Distribution Associated with Landfalling Tropical Cyclones over the Eastern United States. \emph{Mon. Wea. Rev.}, 135, 2185-2206.

\item Hopsch, S. B., C. D. Thorncroft, K. Hodges, and A. Aiyyer, 2007: West African Storm Tracks and Their Relationship to Atlantic Tropical Cyclones. \emph{J. Clim.}, 20, 2468-2483.

\item Aiyyer, A., and C. D. Thorncroft, 2006: Climatology of Vertical Wind Shear over the Tropical Atlantic. \emph{J. Clim.}, 19, 2969-2983.

\item Corbosiero, K. L., J. Molinari, A. R. Aiyyer, and M. L. Black, 2006: The Structure and Evolution of Hurricane Elena (1985). Part II: Convective Asymmetries and Evidence for Vortex Rossby Waves. \emph{Mon. Wea. Rev.}, 134, 3073-3091. 

\item Mekonnen, A., C. D. Thorncroft, and A. R. Aiyyer, 2006: Analysis of convection and its association with African easterly waves. \emph{J. Clim.}, 19, 5405-5421.

\item Lapenis, A., A. Shivdenko, D. Shepaschenko, S. Nilsson, and A. Aiyyer, 2005: Acclimation of Russian forests to recent changes in climate. \emph{ Global Change Biology}, 11, 2090-2102.

\item Nagarajan, B., and A. Aiyyer, 2004: Performance of the ECMWF operational analyses over the tropical Indian ocean. \emph{Mon. Wea. Rev.}, 132, 2275-2282. 

\item Aiyyer, A. R., and J. Molinari, 2003: Evolution of Mixed Rossby Gravity Waves in Idealized MJO Environments. , \emph{J. Atmos. Sci.}, 60, 2837-2855.

\end{ilist}
