\section*{Education}

\begin{tlist}


\item[2003] PhD \hspace{3mm} Atmospheric Science \hspace{4mm} State University of New York, Albany
  
      {\small \emph{Committee: John Molinari, Lance Bosart, Lloyd Shapiro, Daniel Keyser, Arthur Loesch}}
      \vspace{2mm}
      
\item[1998] MS  \hspace{5mm} Atmospheric Science \hspace{4mm} State University of New York, Albany
  
        {\small \emph{Committee: John Molinari, Daniel Keyser}}
        \vspace{2mm}
        
\item[1994] MSc \hspace{4mm}  Physics \hspace{25mm} Indian Institute of Technology, Kharagpur
  \vspace{2mm}
  
\item[1992] BSc \hspace{5mm} Physics \hspace{25mm} Indian Institute of Technology, Kharagpur
\end{tlist}

%------------------------------------------------------------------------------
\section*{Employment}

\begin{tlist}
\item[2012\,--\,present] Associate Professor with Tenure
  
  Department of Marine, Earth and Atmospheric Sciences,  North Carolina State University
      \vspace{2mm}

\item[2006\,--\,2012] Assistant Professor

  Department of Marine, Earth and Atmospheric Sciences, North Carolina State University
      \vspace{2mm}

\item[2003\,--\,2006] Research Associate
  
  {\small \emph {PI: Chris Thorncroft}}

  State University of New York, Albany
  
  
\end{tlist}

%------------------------------------------------------------------------------

\section*{Notable Recognition}

\begin{tlist}

\item[2011] LeRoy and Elva Martin Award For Teaching Effectiveness: NCSU
\item[2009] National Science Foundation Faculty Early Career (CAREER) Proposal
\item[2004] Narayan R. Ghokale Award for Outstanding Research: SUNY Albany
\item[1998] Max A. Eaton Prize: American Meteorological Society.

\end{tlist}



%------------------------------------------------------------------------------
\section*{Editorial Boards and Selected Professional Service}

\begin{tlist}
\item[2021\,--\,present] Associate Editor, Geophysical Research Letters 
\item[2018\,--\,present] Leader, Early Career Geoscience Faculty Workshop 
\item[2016] Co-Chair, Committee of Visitors, National Science Foundation
\item[2003\,--\,present] Peer reviewer: J. Atmos. Sc., Mon. Wea. Rev., J. Clim., Q. J. Roy. Met. Soc., Clim. Dyn., Geo. Res. Letts.
\item[2006\,--\,present] Proposal reviewer: NSF, NOAA
\item[2014\,--\,present] NSF GRFP review panel member
%\item[2008] Max Eaton Award judges panel, 28th Conference on Hurricanes and Tropical Meteorology. Orlando, FL
\item[2006] CMAQ Peer Review, Environmental Protection Agency, Research Triangle Park, North Carolina
\end{tlist}


\section*{Federally funded projects (PI and co-PI)}
\begin{tlist}
\item[NASA] Investigation of the Interaction Between Kelvin Waves and Easterly Waves Using CYGNSS Data  [{\bf \$334,484}]
        \vspace{2mm}

\item[NASA] Multiscale interactions between the MJO, equatorial waves, and the diurnal cycle over the Maritime Continent [{\bf\$383,431}]
              \vspace{2mm}

\item[NSF]  Origin, Storm track Dynamics and Convective Feedback of African Easterly Waves [{\bf \$481,728}]
               \vspace{2mm}

\item[NSF]  US-India International Workshop: Collaborative Science, Research, and Education in Air Quality Measurements, Modeling and Analysis [{\bf \$39,996}]
               \vspace{2mm}

\item[NSF]  CAREER: Dynamics of African Easterly Waves: Integrating phenomenological studies and Mathematical Instruction in Atmospheric Science [{\bf \$556,607}]
               \vspace{2mm}

\item[NOAA] Improving Prediction of Severe Winds, Convection and Heavy Precipitation in the Southeastern United States [{\bf\$375,000}]
               \vspace{2mm}

\item[US DOE] High-Resolution Modeling to Assess Tropical Cyclone Activity in Future Climate Regimes [{\bf\$649,649}]
\end{tlist}


\section*{Technical Skills}
\begin{tlist}
\item[Models]   Weather and Climate modeling of various complexities and process based diagnostics
  
\item[Data analysis]  Extensive experience in  modeled and observed data including reanalysis/reforecast products, daya formats (netcdf, hdf), CMIP outputs, satellite remote sensing data
  
\item[Coding]    Extensive experience in Linux,  modern FORTRAN, NCL, Python
   

\end{tlist}
